TacticToe: Learning the Game of Tactics

### 2018-02-01 tactictoe_jv.tex
recording: wip

% Because our aim is to 
% learn how to prove from existing examples, we record the proofs at 
% an intermediate tactic level closest to the one presented to 
% a user. Since human developers build almost all their proofs from tactics, 
% we believe this is an appropriate level to apply machine learning on.

%More information is contained in tactical scripts than 
%in top-level dependencies on which was based machine-learning guidance in 
%interactive theorem proving so far. Learning from atomic inferences would 
%require better predictions and abstractions of rules to handle the larger 
%search space.

%We first discuss parsing proof scripts and identifying 
%individual tactic calls. We next show how to record tactics calls are recorded 
%with their corresponding goals using a modified proof script.
%The recorded data which consists of tactic-goal pairs creates the raw 
%knowledge 
%necessary for our tactic selection algorithm.

@@

In order to transfer our tactic knowledge between theories, we want to be able 
to re-use the code of a tactic recorded in one theory in an 
other. We also would like to make sure that the code is interpretable and its 
interpretation does not change in the other theory.

Even when developing one theory, the context is continually changing: the open 
modules are different, global and local identifiers are defined and the local 
ones can become out of scope. Therefore, it is unlikely that code extracted 
from proof scripts is interpretable in any part of \holfour.
To solve this issue, we prefix each global identifier by the module where it 
was declared and we recursively unfold local declaration until a local 
identifier can be expressed by through code containing only global identifiers.
We call this process globalization. The result is a standalone \sml code 
executable in any \holfour theories which will be interpreted in the same way 
in the absence 
of side effects.

Therefore, we can guarantee that the behaviour of recorded stateless tactics 
will not change. And because an update on a stateful tactic 
generally increases its strength, our prediction algorithm based on past 
examples will still be reasonably effective.

>>>>

@@

In order to transfer our tactic knowledge between theories, we want to be able 
to re-use the code of a tactic recorded in one theory in an 
other. We also would like to make sure that the code is interpretable and that 
its interpretation does not change in the other theory.

Even when developing one theory, the context is continually changing:
modules are open and local identifiers are defined. Therefore, it is unlikely 
that code extracted from proof scripts is interpretable in any other part of 
\holfour without any post-processing.
To solve this issue, we recursively replace each local identifier by its 
definition until we are able to write any expression with global identifiers 
only. And we prefix each global identifiers by its module.
We call this process globalization. The result is a standalone \sml code 
executable in any \holfour theories.  In the absence of side effects, it is 
interpreted in the same way across theories.
Therefore, we can guarantee that the behavior of recorded stateless tactics 
does not change. And because an update on a stateful tactic 
generally increases its strength, our prediction algorithm based on past 
examples is still reasonably effective in this case.
